|

### 2024-09-16 output/Main_text.Rmd
Update styles to APA 7 format

---
title: "A generalized definition of multidimensional item response theory parameters"
output:
  officedown::rdocx_document:
    tables:
      style: APA_Like_style
    mapstyles:
      Body Text: ['First Paragraph', 'Abstract']
    base_format: bookdown::word_document2
    reference_docx: ../www/Template.docx
    number_sections: no
    keep_md:         no
    fig_width:       4
    fig_height:      4
abstract: |
  In this paper, we generalize the multidimensional discrimination (MDISC) and
  difficulty (MID) parameters in the Multidimensional 2-Parameter Logistic model
  to account for non-identity latent covariances and negatively-keyed items.
  We apply Reckase's maximum discrimination point method to define them in an
  algebraic sense in an arbitrary basis, and then defining such basis to be a
  geometrical representation of the measured construct.
  This results in three different versions of the parameters: The original one,
  based on the item parameters solely, one that incorporates the covariance
  structure of the latent space, and one that uses the correlation structure
  instead. Importantly, we find that the items should be properly represented in
  a test space, distinct from the latent space.
  We also provide a procedure for the geometrical representation of the items in
  the test space, and apply our results to examples from the literature to get a
  more accurate representation of the measurement properties of the items.
  We recommend using the covariance structure version for describing the
  properties of the parameters, and the correlation structure version for
  graphical representation.
  Finally, we discuss the implications of this generalization for other
  multidimensional IRT models and the parallels of our results in common factor
  model theory.
keywords: |
  Multidimensional 2-Parameter Logistic model,
  multidimensional item discrimination, multidimensional item difficulty,
  item vector representation, test space
bibliography: [../www/Multidimensional-parameters-MCLM.bib, ../www/packages.bib]
csl:          ../www/apa-old-doi-prefix.csl
editor_options: 
  chunk_output_type: console
---

@@

library(here)
library(knitr)
library(patchwork)
library(ggplot2)
library(rstudioapi)
library(svglite) # Used by {knitr} and {ggplot2} to render the figure to SVG;
                 #   added to prevent {renv} from reporting inconsistent state.

@@

opts_knit$set(root.dir = ROOT_DIR)
opts_chunk$set(
  echo     = FALSE,
  message  = FALSE,
  cache    = FALSE,
  dev      = "png",
  dpi      = 1200L,
  dev.args = list(type = "cairo-png")
)

@@

# Introduction

@@

# Model formulation

@@

# Linear algebra of non-orthogonal coordinates

@@

## Test space definition

@@

## Direction cosines in the latent space

@@

# Model recasting into polar coordinates

@@

# Point of maximum slope

@@

# Relationship between test space and latent space

@@

# Generalized multidimensional parameters

@@

## Agnostic version

@@

## Covariance-based version

@@

## Correlation-based version

@@

# Vector representation

@@

## Geometric properties of the items

@@

# Graphical representation

@@

## Graphical representation example

@@

```{r example-items-table-out}
#| cache:   false
#| tab_id:  example-items-table-out
#| tab.cap: Item parameters for the graphical example
item_params_output
```

@@

```{r item-plot-out}
#| cache:      false
#| fig.cap:   Item plots in an orthogonal (left) and oblique (right) test space.
#| fig.height: 3.1
#| fig.width:  6.65
plot_orth + plot_oblique

@@

# Application to examples from the literature

@@

```{r empirical-table-Reckase2009-out}
#| cache:   false
#| tab.id:  empirical-table-Reckase2009-out
#| tab.cap: |
#|   Agnostic and covariance-based multidimensional item parameters in
#|   Reckase (2009), with a (rank-complete) three-dimensional covariance matrix.
item_params_output
```

@@

```{r empirical-table-Tezza2018-out}
#| cache:   false
#| tab.id:  empirical-table-Tezza2018-out
#| tab.cap: |
#|   Agnostic and covariance-based multidimensional item parameters in
#|   Tezza et al. (2018).
item_params_output
```

>>>>

---
title: |
  A Generalized Definition of Multidimensional Item Response Theory Parameters
output:
  officedown::rdocx_document:
    tables:
      style: APA_Like_style
      caption:
        style: Image Caption
        sep: ' '
    plots:
      caption:
        sep: ' '
    mapstyles:
      Body Text: ['First Paragraph', 'Abstract']
    base_format: bookdown::word_document2
    reference_docx: ../www/Template.docx
    number_sections: no
    keep_md:         no
    fig_width:       4
    fig_height:      4
abstract: |
  In this paper, we generalize the multidimensional discrimination (MDISC) and
  difficulty (MID) parameters in the Multidimensional 2-Parameter Logistic model
  to account for non-identity latent covariances and negatively-keyed items.
  We apply Reckase's maximum discrimination point method to define them in an
  algebraic sense in an arbitrary basis, and then defining such basis to be a
  geometrical representation of the measured construct.
  This results in three different versions of the parameters: The original one,
  based on the item parameters solely, one that incorporates the covariance
  structure of the latent space, and one that uses the correlation structure
  instead. Importantly, we find that the items should be properly represented in
  a test space, distinct from the latent space.
  We also provide a procedure for the geometrical representation of the items in
  the test space, and apply our results to examples from the literature to get a
  more accurate representation of the measurement properties of the items.
  We recommend using the covariance structure version for describing the
  properties of the parameters, and the correlation structure version for
  graphical representation.
  Finally, we discuss the implications of this generalization for other
  multidimensional IRT models and the parallels of our results in common factor
  model theory.
keywords: |
  Multidimensional 2-Parameter Logistic model,
  multidimensional item discrimination, multidimensional item difficulty,
  item vector representation, test space
bibliography: [../www/Multidimensional-parameters-MCLM.bib, ../www/packages.bib]
csl:          ../www/apa-old-doi-prefix.csl
editor_options: 
  chunk_output_type: console
---

@@

library(here)
library(knitr)
library(patchwork)
library(ggplot2)
library(rstudioapi)
library(svglite) # Used by {knitr} and {ggplot2} to render the figure to SVG;
                 #   added to prevent {renv} from reporting inconsistent state.
library(officer)

@@

opts_knit$set(root.dir = ROOT_DIR)
opts_chunk$set(
  echo     = FALSE,
  message  = FALSE,
  cache    = FALSE,
  dev      = "png",
  dpi      = 1200L,
  dev.args = list(type = "cairo-png"),
  tab.cap.fp_text = fp_text_lite(italic = FALSE, bold = TRUE),
  fig.cap.fp_text = fp_text_lite(italic = FALSE, bold = TRUE)
)

@@

@@

# Model Formulation

@@

# Linear Algebra of Non-Orthogonal Coordinates

@@

## Test Space Definition

@@

## Direction Cosines in the Latent Space

@@

# Model Recasting Into Polar Coordinates

@@

# Point of Maximum Slope

@@

# Relationship Between Test Space and Latent Space

@@

# Generalized Multidimensional Parameters

@@

## Agnostic Version

@@

## Covariance-Based Version

@@

## Correlation-Based Version

@@

# Vector Representation

@@

## Geometric Properties of the Items

@@

# Graphical Representation

@@

## Graphical Representation Example

@@

```{r example-items-table-out}
#| cache:   false
#| tab_id:  example-items-table-out
#| tab.cap: Item Parameters for the Graphical Representation Example
item_params_output
```

@@

```{r item-plot-out}
#| cache:          false
#| fig.cap:   Item Plots in an Orthogonal (Left) and Oblique (Right) Test Space
#| fig.topcaption: true
#| fig.height:     3.1
#| fig.width:      6.65
plot_orth + plot_oblique

@@

# Application to Examples From the Literature

@@

```{r empirical-table-Reckase2009-out}
#| cache:   false
#| tab.id:  empirical-table-Reckase2009-out
#| tab.cap: |
#|   Agnostic and Covariance-Based Multidimensional Item Parameters in
#|   Reckase (2009), With a (Rank-Complete) Three-Dimensional Covariance Matrix
item_params_output
```

@@

```{r empirical-table-Tezza2018-out}
#| cache:   false
#| tab.id:  empirical-table-Tezza2018-out
#| tab.cap: |
#|   Agnostic and Covariance-Based Multidimensional Item Parameters in
#|   Tezza et al. (2018)
item_params_output
```
